\LARGE\singlespacing{\textbf{S1 Appendix} \\ \medskip Spatiotemporal modeling of \emph{Mycobacterium tuberculosis} transmission risks using environmental, clinical, and patient movement data}

### 2024-03-07 doc/paper/supplements.tex

The diffusion constant $D$ is unknown but can be approximated using an empirical relationship between the eddy diffusion coefficient $K$ and the outdoor air exchange rate $AER$ (in air changes/h)\cite{Cheng2011EnvSciTech}
\begin{align}
    K = (0.52 \cdot AER + 8.61\cdot10^{-5}) \cdot V^{\frac{2}{3}},
\end{align}
where $V$ is the volume of the airspace (in m$^3$). We assume that $D \approx K$.

@@

>>>>

The diffusion constant $D$ is unknown but can be approximated using an empirical relationship between the eddy diffusion coefficient $K$ and the outdoor air exchange rate $AER$ (in air changes/h)\cite{Cheng2011EnvSciTech,Foat2020BE}
\begin{align}
    K = (0.52 \cdot AER + 8.61\cdot10^{-5}) \cdot V^{\frac{2}{3}},
\end{align}
where $V$ is the volume of the airspace (in m$^3$). We assume that $D \approx K$.

@@

\section{Additional results}\label{sec:additional-results}

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/data/diagnosed-tb-patients.png}
    \caption{Number of diagnosed TB patients (dark bars) and those suspected of TB (light bars) following symptom screening. Modeled study days in color, other clinic days in October and November in grey.}
    \label{fig:diagnosed-tb-patients}
\end{figure}

\begin{figure}[!htpb]
    \centering
    \includegraphics{results/modeling/model-comparison.png}
    \caption{Difference in the mean risk of infection per clinical attendee between the spatiotemporal and temporal model. Lower: <$-$0.5, Similar: between $-$0.5 and 0.5, Higher: >0.5 percentage points.}
    \label{fig:model-comparison}
\end{figure}
